### 2019-12-03 README.Rmd
reknit README with new plot
Format fixes after RStudio update

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval.after = 'fig.cap'
) 
```
# diffEnrich

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval.after = 'fig.cap'
) 
```
#diffEnrich
